---
title: "TMD Clean up annotations"
author: 'Mohith Reddy Arikatla'
date: "2023-06-22"
output: html_document
---

### Load required datasets

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(plyr)
library(tidyr)
library(forcats)
library(stringr)
library(taxizedb)
```

### Load preliminary datasets

```{r}
# Load preliminary dataset
tmd_data <- read.csv("TMD_Data_2020_full_R_V02.1-Mar.csv", header = T, na.strings = F)

# Substitute "N/A" to "NA"
tmd_data <- data.frame(lapply(tmd_data, function(x) {gsub("N/A",NA, x)}))

# Load proper species names for rows with improper scientific names
JP_species <- read.csv(file="list_species_to_check_JP Updates 02.13.2024.csv",header=TRUE)
```

### Get TaxIDs for all species

```{r}
# Convert both search key and target strings to lower case
search_key <- tolower(JP_species$Weird.name)
target_column <- tolower(tmd_data[, 1])

# Find the indices where search_key matches target_column
matches <- match(search_key, target_column, nomatch = 0)

# Replace values in tmd_data with corresponding values from JP_species
tmd_data[matches,]$scientific_name <- JP_species$NCBI.Tax.name

getTaxID <- function(name_column) {
  species <- name_column
  ids <- name2taxid(species, out_type="summary")
  
  # Convert empty cells to NA
  ids$id[ids$id == ""] <- NA

  return(ids)
}

# Replace tax_id values for rows with missing tax_id in tmd_data
missing_tax_ids <- is.na(tmd_data$taxonomy_id)

missing_names <- tmd_data$scientific_name[missing_tax_ids]

# Get tax_id for missing names
missing_taxIDs <- getTaxID(unique(missing_names))

# Create a named vector (dictionary) for the mapping
tax_id_dict <- setNames(missing_taxIDs$id, missing_taxIDs$name)

# Update the missing tax_ids in tmd_data
tmd_data$taxonomy_id[is.na(tmd_data$taxonomy_id)] <- tax_id_dict[tmd_data$scientific_name[is.na(tmd_data$taxonomy_id)]]

# Remove species called environmental data
tmd_data=tmd_data[!grepl("Environmental samples", tmd_data$scientific_name),] 

# Display how many rows contain tax_id data
missing_tax_ids <- is.na(tmd_data$taxonomy_id)
table(missing_tax_ids)
```

### Merge values from appropriate columns into one column

```{r}
# Merge values from different microbiome columns
tmd_data_v1= tmd_data %>% unite("microbiome",
                                c("euk_microbiome", 
                                  "euk_microbiome.1",
                                  "bac_microbiome"), remove = T,  na.rm = TRUE, sep = ",")

tmd_data_v2= tmd_data_v1 %>% unite("microbiome_water", 
                                   c("bac_microbiome_water", 
                                     "euk_microbiome_water",
                                     "euk_microbe_water"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v3= tmd_data_v2 %>% unite("microbiome_soil", 
                                   c("euk_microbiome_soil", 
                                     "euk_microbiome_soil.1",
                                     "bac_microbiome_soil"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v4= tmd_data_v3 %>% unite("microbiome_soil_type", 
                                   c("euk_microbiome_soil_forest", 
                                     "euk_microbiome_soil_type",
                                     "bac_microbiome_soil_forest"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v5= tmd_data_v4 %>% unite("microbiome_water_fresh", 
                                   c("euk_microbiome_water_fresh.1", 
                                     "bac_microbiome_water_fresh",
                                     "euk_microbiome_water_fresh"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v6= tmd_data_v5 %>% unite("microbiome_water_fresh_wetland", 
                                   c("euk_microbiome_water_fresh_wetland", 
                                     "euk_microbiome_water_fresh_wetland.1",
                                     "bac_microbiome_water_fresh_wetland"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v7= tmd_data_v6 %>% unite("microbiome_water_sediment", 
                                   c("euk_microbiome_water_sediment", 
                                     "euk_microbiome_water_sediment.1",
                                     "bac_microbiome_water_sediment"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v8= tmd_data_v7 %>% unite("microbiome_water_marine", 
                                   c("euk_microbiome_water_marine", 
                                     "euk_microbiome_water_marine.1",
                                     "bac_microbiome_water_marine"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v9= tmd_data_v8 %>% unite("microbiome_host", 
                                   c("euk_microbiome_host", 
                                     "bac_microbiome_host"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v10= tmd_data_v9 %>% unite("microbiome_extreme", 
                                    c("bac_microbiome_extreme", 
                                      "euk_microbiome_extreme",
                                      "euk_microbiome_extreme.1"), remove = T,  na.rm = TRUE, sep = " ")

tmd_data_v11= tmd_data_v10 %>% unite("microbiome_host_human", 
                                     c("euk_microbiome_host_human", 
                                       "bac_microbiome_host_human"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing spore forming ability
tmd_data_v12= tmd_data_v11 %>% unite("spore_forming", 
                                     c("euk_spores", 
                                       "euk_spores.1",
                                       "bac_spores"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing if the organism is an extremophile 
colnames(tmd_data_v12[grepl("extremophile", colnames(tmd_data_v12))])
summary(tmd_data_v12$bac_extremophile)
tmd_data_v13= tmd_data_v12 %>% unite("extremophile", 
                                     c("euk_extremophile", 
                                       "bac_extremophile",
                                       "euk_extremophile.1"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing extremophile type
colnames(tmd_data_v13[grepl("extremophile", colnames(tmd_data_v13))])
tmd_data_v14= tmd_data_v13 %>% unite("extremophile_type", 
                                     c("euk_extremophile_type", 
                                       "euk_extremophile_type.1",
                                       "bac_extremophile.1"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing if the organism is biofilm forming
tmd_data_v15= tmd_data_v14 %>% unite("biofilm_forming", 
                                     c("bac_biofiolm", 
                                       "euk_biofilm"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing if the metabolism source
tmd_data_v16= tmd_data_v15 %>% unite("metabolism_energy", 
                                     c("euk_type_metabolism_energy", 
                                       "bac_metabolism_energy"), remove = T,  na.rm = TRUE, sep = " ")
tmd_data_v17 = tmd_data_v16 %>% unite("metabolism_carbon_source", 
                                      c("euk_type_metabolism_carbon_source", 
                                        "bac_metabolism_carbon_source"), remove = T,  na.rm = TRUE, sep = " ")
tmd_data_v18 = tmd_data_v17 %>% unite("metabolism_electron_source", 
                                      c("bac_metabolism_electron_source", 
                                        "euk_type_metabolism_electron_source"), remove = T,  na.rm = TRUE, sep = " ")
tmd_data_v19 = tmd_data_v18 %>% unite("metabolism", 
                                      c("euk_type_metabolism", 
                                        "bac_metabolism"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing if the organism is a pathogen
tmd_data_v20 = tmd_data_v19 %>% unite("pathogen", 
                                      c("virus_pathogen", 
                                        "bac_pathogen",
                                        "euk_pathogen",
                                        "euk_pathogen.1"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing the host organism type
tmd_data_v21 = tmd_data_v20 %>% unite("pathogen_host", 
                                      c("euk_pathogen_host.1", 
                                        "virus_pathogen_host",
                                        "euk_pathogen_host",
                                        "bac_pathogen_host"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing the host organism location
tmd_data_v22 = tmd_data_v21 %>% unite("pathogen_host_human", 
                                      c("euk_pathogen_host_human", 
                                        "virus_pathogen_host_human",
                                        "bac_host_human"), remove = T,  na.rm = TRUE, sep = " ")

# Combine the columns informing if the organism has antimicrobial activity
tmd_data_v23 = tmd_data_v22 %>% unite("antimicrobial_activity", 
                                      c("bac_antimicrobial", 
                                        "euk_antimicrobial_resistance"), remove = T,  na.rm = TRUE, sep = " ")

# Correct spelling errors
tmd_data_v24=data.frame(lapply(tmd_data_v23, function(x) gsub("Unkown", "Unknown", x)))

# Replace empty strings with NA
tmd_data_v24[tmd_data_v24==""]<-NA

# Solve the case sensitivity issue causing duplicate rows for the same microbe. 
# Remove quotes from scientific names
tmd_data_v24$scientific_name <- gsub("['‘]", "", tmd_data_v24$scientific_name)

# Convert all scientific names to lower case 
tmd_data_v24$scientific_name <- tolower(tmd_data_v24$scientific_name)

# Make a list of unique scientific names
tmd_data_v24_entries=as.data.frame(fct_count(tmd_data_v24$scientific_name))
colnames(tmd_data_v24_entries)=c("scientific_name", "entry_counts")

# Count the number of entries per species to the dataframe
tmd_data_v25=merge(tmd_data_v24_entries, tmd_data_v24, by = "scientific_name")

# Aggregate rows based on scientific name
tmd_data_v26=aggregate(tmd_data_v25[,2:ncol(tmd_data_v25)], by = tmd_data_v25[1],
                       FUN=function(i) paste(i, collapse = " "))

# Change inherently conflicting/mutually exclusive results to "Incongruent" 
tmd_data_v27=tmd_data_v26
tmd_data_v27[] <- lapply(tmd_data_v27, function(x) gsub("Yes No|No Yes", "Incongruent", x))
tmd_data_v27[] <- lapply(tmd_data_v27, function(x) gsub("Eukarya Bacteria/Archaea|Bacteria/Archaea Eukarya|Bacteria/Archaea Virus|Virus Bacteria/Archaea|Eukarya Virus|Virus Eukarya",
                                                        "Incongruent", x))
tmd_data_v28=tmd_data_v27[!(tmd_data_v27$domain=="Incongruent"),]
tmd_data_v28[] <- lapply(tmd_data_v28, function(x) gsub("Algae Fungi|Fungi Algae",
                                                        "Incongruent", x))
tmd_data_v29=tmd_data_v28[!(tmd_data_v28$eukarya_type=="Incongruent"),]

tmd_data_v29[] <- lapply(tmd_data_v29, function(x) gsub("Macrofungi Microfungi|Microfungi Macrofungi",
                                                        "Incongruent", x))
tmd_data_v29[] <- lapply(tmd_data_v29, function(x) gsub("Macroalgae Microalgae|Microalgae Macroalgae",
                                                        "Incongruent", x))
tmd_data_v30 <- tmd_data_v29

# Change scientific name capitalization
tmd_data_v30$scientific_name <- str_to_sentence(tmd_data_v29$scientific_name)

# Keep only unique entries from the columns microbiome and microbiome_water
tmd_data_v30$microbiome <- sapply(tmd_data_v30$microbiome, function(x) paste(unique(unlist(str_split(x," "))), collapse = " "))
tmd_data_v30$microbiome_water <- sapply(tmd_data_v30$microbiome_water, function(x) paste(unique(unlist(str_split(x," "))), collapse = " "))
tmd_data_v31 <- tmd_data_v30

# Move the column taxonomy_id in front of scientific_name
tmd_data_v31 <- tmd_data_v31 %>% relocate(scientific_name, .before=taxonomy_id)

# Write a csv file with the resulting dataframe
write.csv(tmd_data_v31, "tmd_data_v31.csv")
```

### Load curated dataset for vote

```{r}
TMD_Latest <- read.csv("tmd_data_v31.csv", row.names = 1)
```

#### Define exclusive columns (i.e., columns for which there can only be one answer) and take a vote to result in a single answer. 

```{r}
# Exclusive columns - mutually exclusive
exclusive_cols <- c(6,7,8,9,10,11,22,25,26,27,28,29,31,32,33,34,37,38,40,42,44,46,48,57,59,60,61,62,63,64)

# Define a function to read different entries within each exclusive column conduct a vote to result in single value results
take_vote_and_change_to_incongruent <- function(data, entry_count) {
  # Split the string by space
  values <- unlist(strsplit(data, " "))
  
  # Convert values to lowercase
  #values <- tolower(values)
  
  # Remove "NA" from unique values if other values are present
  if (length(unique(values)) > 1) {
    values <- values[values != "NA"]
  }
  
  # Take a vote and choose the major value to represent the row. Else set the values to "Incongruent"
  if (length(values) > 2) {
    vote <- data.frame(table(values))
    order <- vote[order(-vote$Freq),]
    #vote <- reorder(vote$values,vote$Freq)
    if (order$Freq[1] >= floor((length(values)+1)/ 2)){
      values <- order$values[1]
    } else {
      values <- "Incongruent"
    }
  }
  else if(length(unique(values)) > 1) {
    values <- "Incongruent"
  }
  # Join the cleaned values back into a single object
  result <- paste(sort(values), collapse = " ")
  return(result)
}

# Define a function to split and keep unique values
split_and_keep_unique <- function(x) {
  
  # Split the string by space and keep only unique values
  unique_values <- unique(unlist(strsplit(x, " ")))
  unique_values <- sort(unique_values)
  # Join the unique values back into a single string
  result <- paste(sort(unique_values), collapse = " ")
  return(result)
}

# Define a function to split entries, correct spelling errors and sort the values in alphabetical order
clean_and_process_values <- function(x) {
  # Split the string by space
  values <- unlist(strsplit(x, " "))
  
  # Convert values to lowercase
  # Note: Commenting out this line. Uncomment if needed.
  # values <- tolower(values)
  
  # Remove "na" from unique values if other values are present
  if (length(unique(values)) > 1) {
    values <- values[values != "NA"]
  }
  
  # Remove "unknown" from unique values if other values are present
  if (length(unique(values)) > 1) {
    values <- values[values != "Unknown"]
  }
  
  # Capitalize the first letter of each word
  # Note: Commenting out this line. Uncomment if needed.
  # values <- str_to_title(values)
  
  # Replace "NA" with NULL
  if (length(values) == 1 && values[1] == "NA") {
    values <- NA
  }
  
  # Join the cleaned values back into a single object
  result <- paste(sort(values), collapse = " ")
  return(result)
}

```

#### Apply the custom functions to every cell in the data frame

```{r}

# Use the vote function on exclusive columns 
TMD_Latest[,exclusive_cols] <- as.data.frame(apply(TMD_Latest[,exclusive_cols], 2, function(x) sapply(x, take_vote_and_change_to_incongruent)))

#write.csv(TMD_Latest,file="TMD_V02.csv")

# Use the function to split strings with spaces and keep unique values
TMD_Latest[,2:64] <- as.data.frame(apply(TMD_Latest[,2:64], 2, function(x) sapply(x, split_and_keep_unique)))

#write.csv(TMD_Latest,file="TMD_V03.csv")

# Use the function to correct spelling errors and sort the values in alphabetical order
TMD_Latest[,2:64] <- as.data.frame(apply(TMD_Latest[,2:64], 2, function(x) sapply(x, clean_and_process_values)))

write.csv(TMD_Latest,file="TMD_V04.csv")
```

```{r}
TMD_Latest <- read.csv(file = "TMD_V04.csv",row.names = 1)
```

### Subset data per domain

#### Establish column groups to subset data for each domain

```{r}
TMD_col1to6 <- TMD_Latest[,1:6]
TMD_col7to71 <- TMD_Latest[,7:71]
superkingdom <- NA

TMD_skAdded <- cbind(TMD_col1to6,superkingdom,TMD_col7to71)

TMD_Latest <- TMD_skAdded

# Extremophile columns
extremophile <- c(35,36)

# Microbiome host
microbiome_host_human <- 56
microbiome_host <- c(55,microbiome_host_human)

# Microbiome soil
microbiome_soil <- 19

# Microbiome water
microbiome_water_marine <- 17
microbiome_water_fresh <- 15
microbiome_water_sediment <- 18
microbiome_water <- c(14,microbiome_water_marine, microbiome_water_fresh, microbiome_water_sediment)

# Microbiome extreme
microbiome_extreme <- 21

# Microbiome columns
microbiome <- c(13, microbiome_host, microbiome_soil, microbiome_water, microbiome_extreme)

# Pathogen host
pathogen_host <- c(42,57)
pathogen <- c(41,pathogen_host)

# Extremophile columns
extremophile <- c(35,36)

# Bacteria columns
bac_col <- c(59,60,extremophile,38,microbiome,pathogen,34,58,51)

# Fungi columns
fungi_col <- c(8,9,extremophile,38,microbiome,pathogen,58,10)

# Eukaryote lifestyle
euk_lifestyle_benthic <- 25
euk_lifestyle <- c(24,euk_lifestyle_benthic)

# Eukaryote secondary structure
euk_secondary_structure_type <- 29
euk_secondary_structure <- c(28,euk_secondary_structure_type)

# Eukaryote antagonism
euk_antagonism_type <- 44
euk_antagonism <- c(43,euk_antagonism_type)

# Eukaryote toxin type
euk_toxin_type <- 50
euk_toxin <- c(49,euk_toxin_type)

# Diatoms
diatom <- c(12,euk_lifestyle,26,27,euk_secondary_structure,euk_antagonism,euk_toxin)

# Eukaryote pigmentation
euk_pigmentation_type <- 31
euk_pigmentation <- c(30,euk_pigmentation_type) 

# Eukaryote locomotion
euk_locomotion_type <- 33
euk_locomotion <- c(32,euk_locomotion_type)

# Extremophile
extremophile_type <- 36
extremophile <- c(35,extremophile_type)

# Eukaryote symbiosis
euk_symbiosis_host <- 40
euk_symbiosis <- c(39,euk_symbiosis_host)

# Eukaryote content
euk_content_list <- 46
euk_content_production <- c(45,euk_content_list)

# Eukaryote UV resistance
euk_uv_resistant <- 47

# Algae columns
algae_col <- c(8,11, diatom, microbiome, 23, euk_pigmentation, euk_locomotion, 34, extremophile, 37, 38, euk_symbiosis, pathogen, euk_content_production, euk_uv_resistant, 51)

# Virus columns
virus_capsid_symmetry <- 65
virus_capsid <- c(64, virus_capsid_symmetry)

virus_col <- c(61,62,63,virus_capsid,pathogen)

microbe_cols_list <- list(bac_col,fungi_col,algae_col, virus_col)
```

#### Add data from Google Gemini

```{r}
Gemini_Archaea <- read.csv("Gemini/Gemini_archaea_listv02_Mar.csv")
Gemini_Virus <- read.csv("Gemini/Gemini_virus_listv02_Mar.csv")
Gemini_Diatom <- read.csv("Gemini/Gemini_diatom_listv02_Mar.csv")
Gemini_Bacteria <- read.csv("Gemini/Gemini_bacteria_listv02_Mar.csv")

# Set source and domain values manually
Gemini_Archaea$source <- "Gemini"
Gemini_Archaea$domain <- "Archaea"
Gemini_Virus$source <- "Gemini"
Gemini_Virus$domain <- "Virus"
Gemini_Diatom$source <- "Gemini"
Gemini_Diatom$domain <- "Eukarya"
Gemini_Diatom$eukarya_type <- "Algae"
Gemini_Bacteria$source <- "Gemini"
Gemini_Bacteria$domain <- "Bacteria"

TMD_Latest$source <- "TMD"

# Combine data from Gemini to the main dataset
Gemini_GhostCols <- rbind.fill(TMD_Latest,Gemini_Archaea) 
Gemini_GhostCols <- rbind.fill(Gemini_GhostCols,Gemini_Diatom) 
Gemini_GhostCols <- rbind.fill(Gemini_GhostCols,Gemini_Bacteria)
Gemini_GhostCols <- rbind.fill(Gemini_GhostCols,Gemini_Virus) 

# Get tax_id for scientific names missing data in Gemini
missing_names <- Gemini_GhostCols[which(is.na(Gemini_GhostCols$taxonomy_id)),]$scientific_name
missing_taxIDs <- clusterProfiler::getTaxID(unique(missing_names))

# Create a named vector (dictionary) for the mapping
tax_id_dict <- setNames(missing_taxIDs$id, missing_taxIDs$name)

# Update the missing tax_ids in tmd_data
Gemini_GhostCols$taxonomy_id[is.na(Gemini_GhostCols$taxonomy_id)] <- tax_id_dict[Gemini_GhostCols$scientific_name[is.na(Gemini_GhostCols$taxonomy_id)]]

TMD_Latest <- Gemini_GhostCols
```

```{r}
#write.csv(TMD_Latest,file="TMD_V05.csv")
TMD_Latest <- read.csv(file = "TMD_V05.csv",row.names = 1)
```

#### Get superkingdom from NCBI Taxa ID

```{r}

taxIDs <- TMD_Latest$taxonomy_id
taxIDs <- na.omit(taxIDs)

classification <- taxizedb::classification(taxIDs)

all_taxaIDs <- c()
all_superkingdoms <- c()

# Loop through each element in classification
for (name in names(classification)) {
    # Check if the element is a data frame
    if (is.data.frame(classification[[name]])) {
        # Find the row where the rank is "superkingdom"
        row_index <- which(classification[[name]]$rank == "superkingdom")
        
        # Check if such a row exists
        if (length(row_index) > 0) {
            # Append the taxa ID value from that row to the vector
            all_taxaIDs <- c(all_taxaIDs, name)
            # Append the corresponding superkingdom value
            all_superkingdoms <- c(all_superkingdoms, classification[[name]]$name[row_index])
        }
    }
}

# Create a dataframe with ID and superkingdom columns
sk_result_df <- data.frame(ID = all_taxaIDs, superkingdom = all_superkingdoms)

for(ID in sk_result_df$ID){
  # Extract the superkingdom value corresponding to the entry
  sk_value <- sk_result_df[sk_result_df$ID == ID, "superkingdom"]
  TMD_Latest$superkingdom[TMD_Latest$taxonomy_id == ID] <- sk_value[1]
}

table(TMD_Latest$superkingdom)
```

```{r}
#write.csv(TMD_Latest,file="TMD_V06.1.csv")
#TMD_Latest <- read.csv(file = "TMD_V06.1.csv",row.names = 1)

#TMD_Latest[TMD_Latest$source == "Gemini" & TMD_Latest$domain == "Eukarya", "eukarya_type"] <- "Algae"
#write.csv(TMD_Latest,file="TMD_V06.2.csv")
TMD_Latest <- read.csv(file = "TMD_V06.2.csv",row.names = 1)
```

#### Subset dataset into separate files per domain

```{r}
queryDomainTMD <- function(microbe, microbe_column_list = microbe_cols_list) {
  
  microbe_cols <- switch(
    microbe,
    "Bacteria" = microbe_column_list[1],
    "Fungi" = microbe_column_list[2],
    "Algae" = microbe_column_list[3],
    "Virus" = microbe_column_list[4]
  )
  
  domain <- switch(
    microbe,
    "Bacteria" = c("Bacteria/Archaea", "Bacteria", "Archaea"),
    "Fungi" = "Eukarya",
    "Algae" = "Eukarya",
    "Virus" = "Virus"
  )
  
  # Print sanity check for microbe_cols
  # print(microbe_cols)
  
  general <- c(1, 2, 3, 4, 5, 6, 7, unlist(microbe_cols), 66, 67, 68, 69, 70, 71, 72, 73)
  
  # Print sanity check for general
  # print(general)
  
  # Create a data frame with the selected columns
  if ("Eukarya" %in% domain) {
    query_data <- TMD_Latest[TMD_Latest$eukarya_type == microbe, general]
  } else {
    query_data <- TMD_Latest[TMD_Latest$domain %in% domain, general]
  }
  
  # Remove rows with all NAs while keeping rows with at least one non-NA value
  query_data <- data.frame(query_data)
  query_data <- query_data[!apply(is.na(query_data), 1, all), ]
  
  # Define the CSV file path
  query_csv_file <- paste0(microbe, "_data.csv")
  
  # Write the selected data to a CSV file
  write.csv(query_data, file = query_csv_file, row.names = FALSE)
  
  # Print a message indicating the file has been saved
  cat("Selected data for", domain, "has been saved to", query_csv_file, "\n")
}

queryDomainTMD(microbe="Virus")
queryDomainTMD(microbe="Algae")
queryDomainTMD(microbe="Fungi")
queryDomainTMD(microbe="Bacteria")

```
